Rotational Spectral Unmixing of Exoplanets:\\Degeneracies between Surface Colors and Geography

### 2017-04-29 paper/main.tex
minor edits

Unmixing the disk-integrated spectra of exoplanets provides a clue to heterogeneous surfaces that we cannot directly resolve in the foreseeable future. 
It is particularly important for terrestrial planets with diverse surface compositions like Earth. 
Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, we point out a mathematical degeneracy between the surface colors and their spatial  distributions. 
Nevertheless, useful constraints on the spectral shape of individual surface types may be obtained from the fact that albedo should be between 0 and 1, depending on the trajectory of the planet in color space.  
We demonstrate the degeneracy and the possible constraints using both mock data based on a toy model of Earth, as well as observations of Earth. 
Despite the severe degeneracy, we are still able to recover an approximate albedo spectra for ocean. 
In general, we find that surfaces are easier to identify when they cover a large fraction of the planet and when their spectra approach zero or unity in certain bands. 
%We find that observing at multiple wavelengths where surfaces albedo is close to 0 or 1 will provide better constraints. 
\end{abstract}

>>>>

Unmixing the disk-integrated spectra of exoplanets provides a clue to heterogeneous surfaces that we cannot directly resolve in the foreseeable future. 
It is particularly important for terrestrial planets with diverse surface compositions like Earth. 
Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, we point out a mathematical degeneracy between the surface colors and their spatial  distributions. 
Nevertheless, useful constraints on the spectral shape of individual surface types may be obtained from the \edit{condition} that albedo should be between 0 and 1, depending on the trajectory of the planet in color space.  
We demonstrate the degeneracy and the possible constraints using both mock data based on a toy model of Earth, as well as observations of Earth. 
Despite the severe degeneracy, we are still able to recover an approximate albedo spectra for ocean. 
In general, we find that surfaces are easier to identify when they cover a large fraction of the planet and when their spectra approach zero or unity in certain bands. 
%We find that observing at multiple wavelengths where surfaces albedo is close to 0 or 1 will provide better constraints. 
\end{abstract}
